Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
affiliations

\jmlryear{2014}
\jmlrworkshop{Neural Connectomics Workshop}
\jmlrauthors{A. Sutera et al}

@@

\author{Antonio Sutera,
        Arnaud Joly,
        Vincent François-Lavet,
        Aaron Qiu, \\
        Gilles Louppe,
        Damien Ernst,
        Pierre Geurts}

>>>>

\jmlryear{2014}
\jmlrworkshop{Neural Connectomics Workshop}

@@

\author{\Name{Antonio Sutera,
    Arnaud Joly,
        Vincent François-Lavet,\\
        Aaron Qiu,
        Gilles Louppe,
        Damien Ernst,
        Pierre Geurts}
  \Email{a.sutera@ulg.ac.be}\\
  \addr Department of EE and CS \& GIGA-R, University of Li\`ege, Belgium}

%\jmlrauthors{A. Sutera et al}
%\shortauthor{A. Sutera et al.}
